### 2017-11-10 prezzy/netsMatterDeck.tex
fixes

%!TEX TS-program = xelatex
\documentclass[10pt,xcolor=dvipsnames,compress]{beamer}
\logo{\includegraphics[height=1cm]{Duke_shield.png}}
\usepackage{beamerthemesplit}
\usecolortheme[cmyk={1.0,.69,0.0,.115}]{structure}
\usetheme[height=11mm]{Rochester}
\setbeamertemplate{items}[ball] 
\setbeamerfont{tablefont}{size=\tiny}
\setbeamerfont{quotefont}{size=\small}

@@

\title[AMEN]{Embracing Network Interdependence in International Relations\thanks{Based upon joint works with Shahryar Minhas (Michigan State University), Peter Hoff (Duke University), Cassy L. Dorff (University of New Mexico), Max Gallop (University of Strathclyde), Juan Tellez (Duke University), Howard Liu (Duke University), \& Margaret Foster (Duke University).}
}
\author 
{Michael D. Ward\\ 
Department of Political Science, Duke University} 
%\vspace[*]{5 cm}
\date{Prepared presentation at the Department of Political Science, Texas A\&M University, November 5, 2017. }

@@

\frame{
  \frametitle{What Exactly Is Third-Order Dependency?}
  \framesubtitle{People Want to Know!}
\begin{itemize}
\item<1> If each node has individual characteristics, 
say $x_i$ and $x_j$ for two nodes.  Then,
$x_i \times x_j$ is the multiplicative product of their nodal characteristics and may be related to their relationship, 
$y_{ij}$.  
Let $x$ be an encoding of whether a node is democratic or not. 
Then, $x_i \times x_j \equiv 1 \iff$ 
\textit{both are democracies}.  This approach is often used in standard analyses as a variable often known as 
\textit{joint democracy}.  In the context of networks, a positive effect from the interaction of $x_i$ and $x_j$ might affect some dyadic variable, such as not being in a militarized dispute against one another---often denoted the democratic peace.  This positive effect is known in network terminology as \textit{homophily}.
Most studies just look at the correlation between aggregated variables, but the proposed approach can more directly estimate the degree of homophily.
\end{itemize}
}

\frame{
  \frametitle{What Exactly Is Third-Order Dependency?}
  \framesubtitle{People Want to Know!}
\begin{itemize}
\item<1> Homophily which stems from nodal characteristics results in certain types of network structures: 1) transitivity, 2) balance, and 3) clustering.  For example, homophily tends to induce a large number of \textit{triads}, since if $i$ is similar to $j$ and as a result has a link with $j$, for the same reason it will share a link with $k$ if $j$ and $k$ are similar, thus creating a triad.  Groups of triads tend to result in \textit{clusters}. This can result in clusters in which many elements in the cluster are not only related to one another but share similar characteristics.  This is known as \textit{stochastic equivalence}.

\item To capture this kind of stochastic equivalence---and other types of triadic dependence---we include a latent representation of nodal characteristics in the regression model.  This allows the network representation in a matrix to be dependent upon how similar these latent characteristics are. These latent nodal characteristics are represented by a type of multiplicative effects that are expressed as $\mathbf{u}_i^\intercal \mathbf{v}_i$.  This captures the third-order dependencies, i.e., the dependencies among triads.
\end{itemize}
}

>>>>

%!TEX TS-program = xelatex
\documentclass[10pt,xcolor=dvipsnames,compress]{beamer}
\usepackage{beamerthemesplit}
\usecolortheme[cmyk={1.0,.69,0.0,.115}]{structure}
\usetheme[height=11mm]{Rochester}
\setbeamertemplate{items}[ball] 
\setbeamerfont{tablefont}{size=\tiny}
\setbeamerfont{quotefont}{size=\small}

@@

\title[AMEN]{Taking Dyads Seriously\thanks{Based upon joint works with Michael Ward (Duke University), Cassy L. Dorff (University of New Mexico), Max Gallop (University of Strathclyde), Juan Tellez (Duke University), Howard Liu (Duke University), \& Margaret Foster (Duke University). This is also part of a broader project involving Peter Hoff (Duke University) and Michael Ward.}
}

\author 
{Shahryar Minhas\\ minhassh@msu.edu \\ s7minhas.com \\
Michigan State University}

\date{Beamer is ugly, this needs to be changed.}

@@

\frame{
  \frametitle{What Exactly Is Third-Order Dependency?}
  \framesubtitle{People Want to Know!}
Too much to read on a slide.
\begin{itemize}
\item<1> If each node has individual characteristics, 
say $x_i$ and $x_j$ for two nodes.  Then,
$x_i \times x_j$ is the multiplicative product of their nodal characteristics and may be related to their relationship, 
$y_{ij}$.  
Let $x$ be an encoding of whether a node is democratic or not. 
Then, $x_i \times x_j \equiv 1 \iff$ 
\textit{both are democracies}.  This approach is often used in standard analyses as a variable often known as 
\textit{joint democracy}.  In the context of networks, a positive effect from the interaction of $x_i$ and $x_j$ might affect some dyadic variable, such as not being in a militarized dispute against one another---often denoted the democratic peace.  This positive effect is known in network terminology as \textit{homophily}.
Most studies just look at the correlation between aggregated variables, but the proposed approach can more directly estimate the degree of homophily.
\end{itemize}
}

\frame{
  \frametitle{What Exactly Is Third-Order Dependency?}
  \framesubtitle{People Want to Know!}
\begin{itemize}
\item<1> Homophily which stems from nodal characteristics results in certain types of network structures: 1) transitivity, 2) balance, and 3) clustering.  For example, homophily tends to induce a large number of \textit{triads}, since if $i$ is similar to $j$ and as a result has a link with $j$, for the same reason it will share a link with $k$ if $j$ and $k$ are similar, thus creating a triad.  Groups of triads tend to result in \textit{clusters}. 
\end{itemize}
}

\frame{
  \frametitle{What Exactly Is Third-Order Dependency?}
  \framesubtitle{People Want to Know!}
\begin{itemize}
\item<1> Stochastic equivalence.
\end{itemize}
}
